An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-31 EconGrowth2.Rnw
Added Martin's notes about interpretation of results.

11. ZA case
CD no e: roughly half c, l
CD with e: roughly half, c, e, importance of l drops to 0
CES no e: 10% c, 25% l ??
CES with e: fig 35 e may be NB
LINEX: one of highest ct parameters (high relative importance of labour eff compared to cap eff)
Does this mean that relative small increases in labour eff can really lift the economy?

@@

Drive towards new insights from our stats tested comparative approach

>>>>

11. ZA case
CD no e: roughly half c, l
CD with e: roughly half, c, e, importance of l drops to 0
CES no e: 10\% c, 25\% l ??
CES with e: fig 35 e may be NB
LINEX: one of highest ct parameters (high relative importance of labour eff compared to cap eff)
Does this mean that relative small increases in labour eff can really lift the economy?

@@

Drive towards new insights from our stats tested comparative approach..

**** Notes for interpretation of results ****

Country interpretation

Comparison Cobb Douglas and CES results.

%++++++++++++++++++++++++++++++
\subsection{United States} 
\label{sec:InterpUS}
%++++++++++++++++++++++++++++++

CD: Energy is unnecessary

CES:

($kl$)$e$: energy is unnec ($\delta$ is 1); also ($el$)$k$ energy is unnec. 
($\delta_1$ is 0);

($le$)$k$ no indication
Relative consistent signal that energy is unnec.

$\sigma$:
capital and energy are complements
labour and energy are subsitutable

%++++++++++++++++++++++++++++++
\subsection{United Kingdom} 
\label{sec:InterpUK}
%++++++++++++++++++++++++++++++

CD: Capital is unnec.

CES:

($kl$)$e$: energy is unnec ($\delta =1$);

($le$)$k$ capital is unnec. ($\delta = 1$);

($ek$)$l$ ($\delta_1 = 0$) energy is unnec.

Thus, inconsistent results, possibly look at different time series 
as massive changes in economic policy in Uk economic history

$\sigma$: energy is not substitutable with capital or labour, totally complementary

%++++++++++++++++++++++++++++++
\subsection{Japan} 
\label{sec:InterpJP}
%++++++++++++++++++++++++++++++

CD: energy is unnec.

CES:

($kl$)$e$; ($le$)$k$; ($ek$)$l$: no indications, all are important.

weak signal that labour is less necessary 
(($kl$)$e$ $delta_1 = 0.86$ and ($ek$)$l$ $\delta = 0.89$)

Thus, inconsistent results.

$\sigma$: labour and energy are complements, capital and energy complements

%++++++++++++++++++++++++++++++
\subsection{China} 
\label{sec:InterpCN}
%++++++++++++++++++++++++++++++

CD: energy not necessary, capital less necessary

CES:

($kl$)$e$: energy is unnec. ($\delta = 1$);

($le$)$k$: labour is unnnec ($\delta_1 = 0$);

($ek$)$l$ energy is unnec. ($\delta_1 \rightarrow 0$)

Strong signal that energy is unnec, but the labour and capital signals are conflicting

$\sigma$: capital and energy is complementary, but labour and energy more substitutable

%++++++++++++++++++++++++++++++
\subsection{South Africa} 
\label{sec:InterpZA}
%++++++++++++++++++++++++++++++

CD: Labour is unnec.

CES:

($kl$)$e$: labour is unnec. ($\delta_1 = 1$);

($le$)$k$ labour is unnec. ($\delta_1 = 0$);

($ek$)$l$ labour is unnec. ($\delta = 1$)

Consistent signal that labour is unnec.

$\sigma$: capital and energy is complementary, labour and energy is substitutable

%++++++++++++++++++++++++++++++
\subsection{Saudi Arabia} 
\label{sec:InterpSA}
%++++++++++++++++++++++++++++++

CD: no indications

CES: no indications, but weak signal that labour is unnec in ($ek$)$l$ ($\delta = 0.93$)

Almost consistent signal that no indocations.

$\sigma$: labour and energy are complements, capital and energy are substitutes

%++++++++++++++++++++++++++++++
\subsection{Iran} 
\label{sec:InterpIR}
%++++++++++++++++++++++++++++++

CD: energy is unnec.

CES:

($kl$)$e$: energy is unnec ($\delta=1$);

($le$)$k$: energy is unnec. ($\delta_1=1$);

($ek$)$l$: labour is unnec. ($\delta=1$)

$\sigma$: labour and energy still complements, 
but not as strong capital and energy complements

%++++++++++++++++++++++++++++++
\subsection{Tanzania} 
\label{sec:InterpTZ}
%++++++++++++++++++++++++++++++

CD: labour in unnec.

CES:

($kl$)$e$: labour is unnec ($\delta_1=0.97$);

($le$)$k$: weak signal that energy is unnec. ($\delta_1=0.92$); 
very weal signal capital is unnec ($\delta=0.84$);

($ek$)$l$: labour is unnec. $\delta=0.96$

Consistent signal that labour is unnec, with exception of one nesting.

$\sigma$: labour and energy complements, capital and energy perfect substitutes

%++++++++++++++++++++++++++++++
\subsection{Zambia} 
\label{sec:InterpZM}
%++++++++++++++++++++++++++++++

CD: labour is unnec; energy is unnec.

CES:

($kl$)$e$: labour is unnec. ($\delta_1=1$); labour is unnec

($le$)$k$: ($\delta_1=0$);

($ek$)$l$: labour is unnec. ($\delta=1$)

Consistent signal that labour is unnec.

$\sigma$: labour and energy complements, not as strong. 
Capital and energy perfect substitutes.

% 
% 
% Discussion of results: How to get better consistent signals?
% - Use CD as starting points and do CES convergence on that basis.
% - Do scatterplots to get range of uncertainty inputs, then re-interpret. delta against sigma plots, as well as delta_1 and sigma_1 plots.
% 
% Thus, to do the fitting well we need to understand:
% - nesting
% - algorithm
% - starting values
% esp. for CES. 
% (Maybe illustrate with one case study such as China what implications are).
% 
% How do we compare witj LINEX results?
% CES is a broader specification of CD, LINEX is not. In LINEX no delta's nor sigmas are generated. Only efficiency terms are generated in LINEX, thus in other words economic growth is only possible by increased efficiency. 
% The efficiency of using energy is driven by capital stock. The objective/growth engine is to increase capital at a rate that is faster then growth in labour and energy.  Increasing labour relative to energy gives a muted benefit. 
% LINEX derived for Germany: only really applicable when energy and capital are complements.
% 
% Discussion in relation to other papers. 
% Problems with other papers:
% - If not giving you all parameters
% - Not explain nesting approach 
% - No CI on data
% 
% 
% Economic interpretation (revisit after scatterplot information)
% Developed economies: Capital and energy is complementary (US: labour and energy substitutable)
% NICs: Capital and energy complementary, but labour and energy more substitutable
% OPEC: Labour and energy complementary (mixed results on capital and energy)
% LDCs: Labour and energy complementary, Capital and energy perfect substitutes.
%
